Open-Set Domain Adaptation through Self-Supervision

### 2022-02-11 paper/main.tex
Picture???
Abastract section updated

%%%%%%%%% ABSTRACT
\begin{abstract}
  Performance loss over domain change is a common problem in machine learning applications.
  Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
  In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
  Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
\end{abstract}

@@

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
  In machine learning applications, domain adaptation (DA) techniques try to mitigate the problem of having different domains in the training and test data.
  Another common problem is represented by the presence of more semantic classes in the test data, which are unknown
  and completely new to the developed models. The latter problem comes under the name of novelty or anomaly detection.
  In real world scenarios, it is becoming extremely common suffering of both problems.
  \textit{Open-Set Domain Adaptation (OSDA)} methods try to tackle these problems by jointly adapting a labeled source domain to an unlabeled target domain
  while performing novelty detection. We propose a new method leveraging a self-supervised technique, rotation recognition, constisting in first performing
  novelty detection on the target data and then aligning the two domains avoiding potential negative adaptation.
  Furthermore, we assess the performance using a new metric which represents in a balanced way the ability to jointly solve the two problems.
  Experiments conducted on the Office-Home benchmark show interesting results and method effectiveness.

  % Performance loss over domain change is a common problem in machine learning applications.
  % Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
  % In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
  % Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
\end{abstract}

@@

\begin{figure*}
  \includegraphics[width=\textwidth ]{scheme.png}
  \caption{\label{fig:separation} Schema representing the target images separation process}
\end{figure*}
